### 2024-08-07 Paper.tex
english abstract

The abstract should state briefly the general aspects of the subject and the main concolusions.  The length of abstract should bo no more than 200 word and  should be typed be with 10 pts.

 \bigskip
Keywords: keyword should be chosen that they best describe the contents of the paper and should be typed in lower-case, except abbreviation. Keyword should be no more than 6 word

>>>>

The high population in Indonesia results in long queues in various public services or consumer services. Customers have to come to the place to take a queue number and wait for their turn; the longer the queue, the longer the waiting time required. This is inefficient and causes a lot of time to be wasted just waiting in line. If queue numbers can be obtained online and monitored online, it can reduce wasted time. With a virtual queue application, it is possible to shorten physical queues by queuing virtually, viewing ongoing queues, and booking places. In the development of this application, the framework used is NestJS and PrismaJS by implementing RESTful API, Object Relational Mapping, and avoiding Anti-Patterns. The NestJS framework supports the creation of monolithic and microservice-architecture applications. After the application is built in a monolithic architecture, it can be easily migrated to a microservice architecture when the application usage is almost reaching the user load limit.

 \bigskip
 Keywords: NestJS, PrismaJS, Anti-Pattern, Queue, Backend, REST
